---
title: 'Homework 3: Odds Ratios and Relative Risk'
subtitle: "STAT 244NF: Infectious Disease Modeling"
author: "YOUR NAME HERE"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

## Instructions:

1.  Please replace "YOUR NAME HERE" under author above with your name before you knit your final document for submission.
2.  All of your homework needs to be completed in this document, whether it requires R or just typed responses. As we incorporate more statistical computing into the course, it will be important that you are comfortable with R Markdown, so start now. Remember that R Markdown gives us a convenient framework for reproducible statistical reports because it contains a complete record of our analyses and conclusions.
3.  You may knit to PDF, HTML, or Word (click on the drop-down menu for Knit to choose the file output type).
4.  Before submitting your work, please make sure the knitted file is well organized, legible, and looks the way you expect!
5.  Please include the names of any classmates with whom you worked on this homework, as well as any external resources that you might have used.
6.  This homework assignment is **due on Friday, February 16, 2024 and should be submitted to Gradescope**.

-   *Collaborators:*

-   *External resources:*

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
```

## Infectious Disease Outbreak

An infectious disease outbreak has been reported in a small town. Investigators followed up with all residents in the town and identified potential exposures, including a local festival.

The simulated data for this outbreak are included in the R project for this homework assignment. Assuming you pulled the file from Github as we have been doing in class for R labs, you should be able to directly run the following code to load the data into R.

```{r}
outbreak <- read.csv("STAT244NF_HW3_town_outbreak.csv")
```

Here is the description of the variables in the data set:

\`resident_id\`: a unique identifier for each resident in the small town

\`festival\`: an indicator variable for whether the resident attended the festival

\`case\`: indicator variable for whether the resident became infected

### Question ID 1. Both relative risk and odds ratio are defined in terms of probabilities related to exposure/non-exposure. What constitutes the "exposure" of interest in this study? What about "non-exposure"?

### Question ID 2. Calculate the following probabilities based on the data in `id_outbreak`.

(a) $P(\text{disease}|\text{exposure})$

```{r}

```

(b) $P(\text{disease}|\text{non-exposure})$

```{r}

```

(c) Calculate the relative risk associated with this outbreak.

```{r}

```

(d) Interpret the relative risk you calculated.

(e) Calculate the odds ratio associated with this outbreak.

```{r}

```

(f) Interpret the odds ratio you calculated.

### Question ID 3. Binomial logistic regression

(a) Fit a logistic regression model with only an intercept to these data. Remember to use the `glm` function and to specify `family` argument in the `glm` function as `binomial`. Assign the model fit to `outbreak_binom` and print the summary of the model fit.

```{r}

```

(b) What is the estimate of the intercept? Exponentiate this estimate.

```{r}

```

(c) What is the interpretation of the value you calculated in (b)? Explain in one sentence.

(d) Find a 95% confidence interval for your answer in (b). Please interpret this interval in context.

```{r}

```

(e) Using the results from your logistic regression model, find the appropriate value to replace "X" in the following sentence:

Among residents in this small town, the mean odds of infection among individuals who attended the festival is X times that for individuals who did not attend the festival.

```{r}

```

(f) Find the 95% confidence interval corresponding to your answer in (e). Interpret this interval in context.

```{r}

```

(g) Given your answer in (f), do you conclude the local festival is a likely source of infection? Why or why not? Defend your answer in 1-3 sentences.
